Assimilating disturbance: Toward real-time monitoring and forecasting

### 2023-02-01 supplemental.Rmd
formatting

```{r calibration,fig.cap="Predicted and observed woody biomass, leaf biomass, and NEE at US-Me2",echo=FALSE}
load("fit.RData")

@@

```{r parameters,echo=FALSE}
param.names = c("LUE","GAMMA","tauS","tauW","Av","sd_NEE","sd_leaf","sd_wood")
param.desc = c("Light Use Efficiency","Fraction of GPP allocated to autotrophic respiration","Soil C residence time","Wood C residence time","Fraction of NPP allocated to leaves","NEE standard deviation","leaf C standard deviation","wood C standard deviation")
param.table = cbind(param.names,param.desc,mle$par)
colnames(param.table) <- c("Parameter","Description","Value")
knitr::kable(param.table,caption="Calibrated model parameters")
```

>>>>

```{r calibration, echo=FALSE, fig.asp=1.25, fig.cap="Predicted and observed woody biomass, leaf biomass, and NEE at US-Me2"}
load("fit.RData")

m = matrix(1:3,nrow=3,byrow = TRUE)
layout(m)

@@

```{r parameters, echo=FALSE}
param.names = c("LUE","GAMMA","tauS","tauW","Av","sd_NEE","sd_leaf","sd_wood")
param.desc = c("Light Use Efficiency","Fraction of GPP allocated to autotrophic respiration","Soil C residence time","Wood C residence time","Fraction of NPP allocated to leaves","NEE standard deviation","leaf C standard deviation","wood C standard deviation")
param.table = cbind(param.names,param.desc,format(mle$par,digits=3,scientific=TRUE))
colnames(param.table) <- c("Parameter","Description","Value")
knitr::kable(param.table,caption="Calibrated model parameters")
```
